Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
sec4
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

In this section we describe the extensions to existing Ceph services that
allow for reusability.

{Lua Integration.} Because of limited space we describe our extensions
generally, but we have explicitly added the ability to use Lua to specify
the customizations. Lua is great because..., and let's us save and version
interfaces.

The other two advantages, that Lua leaves a small memory footprint and
that it is secure, are discussed at length in 
\cite{ierusalimschy_programming_2006,neto:dls14-luaos}. In short, Lua
provides relatively robust sandbox capabilities for protecting the

>>>>

In this section we describe how Malacology exposes and builds upon existing
services within Ceph. While we strive for implementation independent
approaches within Malacology, our prototype implementation makes heavy use of
the embedded language Lua to enable dynamic features without relying on
complex and heavy-weight code generation techniques.

{\bf Lua integration.}
Supporting dynamic reconfiguration and programmabiilty is critical in real
systems that must adapt to a changing environment where potentially
conflicting policies arise. We've adopted Lua as a scripting language to
implement dynamic components in Malacology.  Lua is a portable, embedded
scripting language that offers superious performance and productivity
trade-offs, including a JIT-based implementation that is well known for near
native performance. Lua has been used extensively in game engines, and systems
research \cite{neto:dls14-luaos}, including storage systems where it has been
effectively used both on
\cite{grawinkel:pdsw2012-lua,watkins2013:bdmc13-in-vivo} and off
\cite{sevilla:sc15-mantle} the performance critical path.
